---
title: "linear model from Web"
author: "Giselle Gonzalez"
date: "summer 2024"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

# Methods
all variables are numerical, so we use num~num for all three parts


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### descriptive results 

### scatterplot

```{r}
plot(SIMS~ARM,data=data)
```
  
This shows that the the stronger your arm strength is the higher the sims gets

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

  This correlation shows that because since 0.6860 is a positive it means that the higher your strength the higher the sims because if the correlation was a negative it would decrease.


### Inferential  (Build model.1)

  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
#### scatterplot with model fit
```{r}
plot(SIMS~ARM,data=data)
abline(model.1, col='red')
```


This p-value for the intercept and slope are  0.00000000000000022 we reject the null because its smaller then 0.05
#### Predict at target point

```{r}
newdata = data.frame(ARM = 88, GRIP=94)
predict(model.1, newdata, interval='pred')
```

the sims prediction for ARM=88 is 0.7, the prediction interval is (-1.73, 3.14)

  

## Model 2 SIM~GRIP

### descriptive results - scatterplot

```{r}
plot(SIMS~GRIP,data=data)
```

This shows that the more grip STRENTH YOU HAVE IT GOES UP  WHICH MEANS THE simulation GOES UP AS WELL


### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```

This shows that since your grip is strong the simulation will be positive 

### Inferential  (Build model.2)
  
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```  
#### scatterplot with model fit
```{r}
plot(SIMS~GRIP,data=data)
abline(model.2, col='red')
```

This p-value for the intercept and slope are  0.00000000000000022 


#### predict model.2 at target point

```{r}
newdata = data.frame(ARM = 88, GRIP=94)
predict(model.2, newdata, interval='pred')
```
 the sims prediction for GRIP=94 is -0.5, and the prediction interval is (-3.10, 2.03)


## Model 3 SIM~ARM+GRIP

### Numerical results
```{r}

df= data.frame(SIMS=data$SIMS,GRIP=data$GRIP, ARM=data$ARM)
cor(df)
```


CORRELATION MATRIX SHOWS THAT SIMS CORRELATES WITH GRIP AND ARM: AND GRIP CORRELATES WITH SIMS 


### Numerical results (cor)
```{r}
cor(SIMS~ARM+GRIP,data=data)
```
 this is the correlation between the sims score and the two variables arm and grip
  
### Inferential  (Build 2-dimentional model.3)


```{r}
model.3 = lm(SIMS ~ ARM + GRIP, data=data)
summary.lm(model.3)
```

 pvalue from the F-statistics is 0.000000000000002, this means the data fits the model
 INTERCEPT P VALUE IS 0.000000000000002
 ARM P VALUE IS 0.00000001
 GRIP PVALUE IS 0.00004
 THEY ARE ALL LOWER THE 0.05
 
 p-value 0.000000000000002 from the model parameters: intercept, coefficient of arm and COEFFICIENT  of grip 
 

#### predict model.3 at target point

predict interval of sims given a value of 94 for grip and 88 for arm

```{r}
newdata = data.frame(GRIP=94, ARM=88)
predSIMS = predict(model.3, newdata, interval = 'pred')
print(predSIMS)
```
The predicted sims score for grip=94 , arm=88 is 0.150
the interval prediction are (-2.13, 2.43)



## Comparing nested models ANOVA Test

### Model.1 vs Model.3

```{r}
model.1=lm(SIMS ~ ARM, data=data)
anova(model.1, model.3)
summary.lm(model.1)
```

  the anova shows that there is a difference in the models the pvalue is 0.000004  
The model 2 : Sim~arm +grip is better than model 1 sims~arm because the rss is 218 and the rss in model 2 is 188

### Model.2 vs Model.3

```{r}
model.2=lm(SIMS ~ GRIP, data=data)
anova(model.2, model.3)
summary.lm(model.1)
```

Model SIM~ARM+GRIP is better then model sims~grip because the rss is lower(188) 
  the pvalue is 0.000000014


## Informally compare Model.1 with model.2

```{r}
summary.lm(model.1)
summary.lm(model.2)
```

model 1 sims~arm is better then model 2 sims~grip because the residual for model 1 was lower than model 2


