---
title: "linear model from Web"
author: "Giselle Gonzalez"
date: "summer 2024"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

# Methods
all variables are nummerical, so we use num~num for all three parts


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### descriptive results 

### scatterplot

```{r}
plot(SIMS~ARM,data=data)
```
  
This shows that the the stronger your arm strength is the higher the sims gets

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

  This correlation shows that because since 0.6860 is a positive it means that the higher your strength the higher the sims because if the correlation was a negative it would decrease.


### Inferential  (Build model.1)

  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
#### scatterplot with model fit
```{r}
plot(SIMS~ARM,data=data)
abline(model.1, col='red')
```


This pvalue for the intercept and slope are  

#### Predict at target point

```{r}
newdata = data.frame(ARM = 88, GRIP=94)
predict(model.1, newdata, interval='pred')
```

the sims prediction for ARM=88 is 0.7, the prediction interval is (-1.73, 3.14)

  

## Model 2 SIM~GRIP

### Now add in scatterplot


### Numerical results 


### Inferential  (Build model.2)
  

#### predict model.2 at target point

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

`
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

